\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-07 casestudies.tex
added extent manager internals figure
added a section on exemplary case, partially through methodology

@@

>>>>

\CHComment{With the newly added section on exemplary case, perhaps we could re-organize this section? A couple of suggestions: 1) very briefly summarize the three cases and highlight the success stories in the introduction section; 2) move the detailed description of Table Migration and Service Fabric into the experience section.}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=\linewidth]{img/extent_manager}
\caption{Internal components of the Extent Manager in Azure Storage vNext.}
\label{fig:extentmanager}
\end{figure*}

### 2015-09-07 methodology.tex
added a section on exemplary case, partially through methodology

\subsection{Modeling the environment}
\label{sec:method:model}

@@

\subsubsection{Creating a test harness using \psharp}
\label{sec:method:model:harness}

@@

The \texttt{ExtentManager} is a wrapper machine and is used to connect the \psharp modeled code with the legacy \csharp code. A typical wrapper machine contains a handle (as a field) to the system component that is being wrapped (in our case the real Extent Manager object) and the event handlers are responsible for translating any received events to method calls in the real code that is being tested. The \texttt{ExtentManager} is accompanied by a mocked version of the real Network Engine class. The real Extent Manager is communicating with the outside world via remote procedure calls, but in \psharp harness we want to capture this communicating and expose it as calls to \psharp communicating primitives. This is discussed in detail in Section~\ref{sec:method:model:dispath}.

@@

\subsubsection{Using method dispatch for modeling}
\label{sec:method:model:dispath}

\begin{figure}[t]
\begin{lstlisting}
// Public interface of the real network engine
class NetworkEngine {
  public virtual void SendMessage(Socket s, Message msg);
  public virtual void EnqueueMessage(Message msg);
}

// The mocked network engine used during testing
class MockedNetEngine : NetworkEngine {
  ExtentManager EM; // Handle to actual system under test
  MachineId Env; // Handle to modeled environment

  public MockedNetEngine(ExtentManager em, MachineId env) {
    this.EM = em;
    this.Env = env;
  }

  public override void SendMessage(Socket s, Message msg) {
    PSharpRuntime.Send(this.Env, new MsgEvent(), s, msg);
  }

  public override void EnqueueMessage(Message msg) {
    this.EM.ProcessMessage(msg);
  }
}
\end{lstlisting}
\vspace{-2mm}
\caption{The mocked network engine used for testing the Azure Storage vNext system.}
\label{fig:enginecode}
%\vspace{-2mm}
\end{figure}

>>>>

\subsection{Testing Target}
\label{sec:method:wrap_target}

The testing target in this case is Extent Manager, from the real vNext codebase. It is wrapped inside a \psharp machine in the test setup.

As shown in Figure~\ref{fig:wrap_target}, the \texttt{ExtentManagerMachine} is a wrapper machine and is used to connect the \psharp modeled code with the legacy \csharp code. A typical wrapper machine contains a handle (as a field) to the system component that is being wrapped (in our case the real Extent Manager object) and the event handlers are responsible for translating any received events to method calls in the real code that is being tested. The \texttt{ExtentManager} is accompanied by a mocked version of the real Network Engine class. The real Extent Manager is communicating with the outside world via remote procedure calls, but in \psharp harness we want to capture this communicating and expose it as calls to \psharp communicating primitives. This is discussed in detail in Section~\ref{sec:method:model:dispath}.

\begin{figure}[t]
\begin{lstlisting}
// Wrapping the target vNext component in P#
class ExtentManagerMachine : Machine {
  private ExtentManager extMgr; // target vNext component

  void Init()
  {
    extMgr = new ExtentManager();

    extMgr.netEngine = new MockedNetEngine(); // mock network
    extMgr.SkippingJournal = true; // skip persistence
    extMgr.IsMockingTimer = true;	 // disable internal timer
  }

  [OnEventDoAction(typeof(MessageFromExtentNodeEvent), nameof(DeliverMessageAction))]

  private void DeliverMessageAction()
  {
    var msg = (CommandMessage)this.Payload;
    // relay messages from Extent Node to Extent Manager
    extMgr.ProcessSingleMessage(msg);
  }
}
\end{lstlisting}
\vspace{-2mm}
\caption{Wrapping vNext Component in \psharp.}
\label{fig:wrap_target}
%\vspace{-2mm}
\end{figure}

\subsubsection{Relaying Inbound Messages}
\label{sec:method:model:incoming}

Messages from mocked Extent Nodes are delivered to the wrapper \psharp machine as events. The wrapper machine processes such events and relay the corresponding messages to its internal Extent Manager (\emph{extMgr.ProcessSingleMessage}). From the perspective of Extent Manager, these messages are no different from these from real Extent Nodes.

%\subsubsection{Using method dispatch for modeling}
\subsubsection{Proxying Outbound Messages}
\label{sec:method:model:dispath}

%\begin{figure}[t]
%\begin{lstlisting}
%// Public interface of the real network engine
%class NetworkEngine {
  %public virtual void SendMessage(Socket s, Message msg);
  %public virtual void EnqueueMessage(Message msg);
%}
%
%// The mocked network engine used during testing
%class MockedNetEngine : NetworkEngine {
  %ExtentManager EM; // Handle to actual system under test
  %MachineId Env; // Handle to modeled environment
  %
  %public MockedNetEngine(ExtentManager em, MachineId env) {
    %this.EM = em;
    %this.Env = env;
  %}
  %
  %public override void SendMessage(Socket s, Message msg) {
    %PSharpRuntime.Send(this.Env, new MsgEvent(), s, msg);
  %}
  %
  %public override void EnqueueMessage(Message msg) {
    %this.EM.ProcessMessage(msg);
  %}
%}
%\end{lstlisting}
%\vspace{-2mm}
%\caption{The mocked network engine used for testing the Azure Storage vNext system.}
%\label{fig:enginecode}
%%\vspace{-2mm}
%\end{figure}

\begin{figure}[t]
\begin{lstlisting}
// network interface in vNext codebase
class NetworkEngine {
  public virtual void SendMessage(Socket s, Message msg);
}

// mocked network for capturing Extent Manager messages
class MockedNetEngine : NetworkEngine {
  public override void SendMessage(Socket s, Message msg) {
    // capture and relay Extent Manager messages
    PSharpRuntime.Send(this.Environment, new MessageFromExtentManagerEvent(), s, msg);
  }
}
\end{lstlisting}
\vspace{-2mm}
\caption{Mocked Network Engine.}
\label{fig:enginecode}
%\vspace{-2mm}
\end{figure}

\subsection{Mocking Extent Node}
\label{sec:method:mock_en}

briefly describe mocked repair logic.

briefly describe mocked sync logic

%\begin{figure}[t]
%\begin{lstlisting}
%// Wrapping the target vNext component in P#
%class ExtentNodeMachine : Machine {
  %private ExtentNode.ExtentCenter extCtr; // real vNext component
%
	%[OnEventDoAction(typeof(RepairExtentRequestEvent), nameof(ProcessRepairExtentRequest))]
	%[OnEventDoAction(typeof(DownloadExtentRequestEvent), nameof(ProcessDownloadExtentRequestEvent))]
	%[OnEventDoAction(typeof(DownloadExtentResponseEvent), nameof(ProcessDownloadExtentResponseEvent))]
	%[OnEventDoAction(typeof(TimerTickEvent), nameof(ProcessExtentNodeSyncEvent))]
%
  %void ProcessRepairExtentRequest()
  %{
    %var source = GetRepairSourceMachine(this.Payload);
    %PSharpRuntime.Send(source, new DownloadExtentRequestEvent(), this.Payload);
  %}
%
  %void ProcessDownloadExtentRequestEvent()
  %{
	  %var destination = GetRepairDestinationMachine(this.Payload);
    %var ext_id = GetExtentID(this.Payload);
    %
		%Extent ext;
    %if (extCtr.TryGet(ext_id, out ext))
      %PSharpRuntime.Send(destination, new DownloadExtentResponseEvent(), ext);
  %}
%
  %void ProcessDownloadExtentResponseEvent()
  %{
    %var ext = (Extent)this.Payload;
    %extCtr.AddExtent(ext);
%
    %this.Monitor<RepairMonitor>(new NotifyExtentRepairCompletion(), this.NodeID);
  %}
%
  %void ProcessExtentNodeSyncEvent()
  %{
    %var sync = new ExtentNodeSync(this.NodeID);
    %extCtr.Extents.ForEach(ext =>
      %{
        %var rec = new ExtentRecord(ext.ExtentID, ext.Length, ext.Sealed);
        %sync.ExtentRecs.Add(rec);
      %});
    %PSharpRuntime.Send(this.NameNode, new NameNodeMessageEvent(), sync);
  %}
%}
%\end{lstlisting}
%\vspace{-2mm}
%\caption{Mocked Extent Node.}
%\label{fig:mocked_en}
%%\vspace{-2mm}
%\end{figure}

\begin{figure}[t]
\begin{lstlisting}
// Mocking Extent Node in P#
class ExtentNodeMachine : Machine {
  // use real vNext component whenever appropriate
  private ExtentNode.ExtentCenter extCtr;

  [OnEventDoAction(typeof(RepairExtentRequestEvent), nameof(ProcessRepairExtentRequest))]
  [OnEventDoAction(typeof(TimerTickEvent), nameof(ProcessExtentNodeSync))]

  // extent repair logic
  void ProcessRepairExtentRequest()
  {
    var source = GetRepairSourceMachine(this.Payload);
    PSharpRuntime.Send(source, new DownloadExtentRequestEvent(), this.Payload);
  }
  ...

  // extent node sync logic
  void ProcessExtentNodeSync()
  {
    var sync = new ExtentNodeSync(this.NodeID);
    extCtr.Extents.ForEach(ext =>
      {
        sync.ExtentRecords.Add(new ExtentRecord(ext));
      });
    PSharpRuntime.Send(this.ExtentManagerMachine, new MessageFromExtentNodeEvent(), sync);
  }
}
\end{lstlisting}
\vspace{-2mm}
\caption{Mocked Extent Node.}
\label{fig:mocked_en}
%\vspace{-2mm}
\end{figure}

%\subsection{Modeling the environment}
\subsection{Test Harness}
\label{sec:method:model}

@@

%\subsubsection{Creating a test harness using \psharp}
\subsubsection{Orchestrating Machines}
\label{sec:method:model:harness}

@@

@@
